\begin{conclusion}
In the~first chapter, Flutter framework as a~new promising cross-platform framework was introduced. How the framework works, its philosophy ``everything is a widget'' was explained and~different approaches of state management were covered. 

Next chapter was focused on introducing proposed application, its designing process, prototyping and user testing. Low-Fidelity and High-Fidelity prototypes were created to verify proposed design. Both prototypes are also included along with final implementation in the~appendix. 

In the~implementation chapter, more details were covered and also several popular packages and solutions within Flutter community were introduced. In the~end, the~\textit{Android} version of the~Coffee Time application was successfully tested and it was released for download. 

\section{Next Steps}
Coffee Time is for sure not ``feature-complete'' and there is plenty of space for improvements. Ongoing future development is planned to obtain more experience with Flutter framework and bring an~even better, feature ``rich'', application.

Next possible features and steps are:

\begin{itemize}
    \item Add missing feature ``searching cafes in custom location''.
    \item To synchronize favourite cafes.
    \item A~better map view with more information in it.
    \item Optimise application performance, responsivity and adaptability to different form factors (mobile phones, tablets, \ldots), screen sizes and resolutions.
    \item Add full \textit{iOS} support. This includes redesign of the application to more modern cross-platform look. 
    \item As an~experiment, build application also for web and desktop platform.
\end{itemize}

\subsection{Personal Author's Note in the End}
\begin{quote}
I really believe that Flutter is a~promising framework which increasingly gains on popularity and in the closest future there will be more opportunities as the~framework will get adopted by larger companies. In the~contrast with Xamarin, my subjective opinion is that the~Flutter development workflow is faster, more convenient and easier to use. Of course, as with every new popular framework, there is no guarantee that Flutter will be truly the right solution in the future. But I am convinced that, at this moment, Flutter is stable to use as a production-ready framework. If the application does not use very specific platform features, Flutter can be used without any hesitation.
\end{quote}
\end{conclusion}